---
title: "Diamond Price Prediction by Shiny App"
author: "Mai Duong"
date: "11/10/2017"
output: ioslides_presentation
runtime: shiny
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction
### Purpose:
#### Use Shiny to built an Shiny App:
- To predict price of Diamond by Carat and X
- To compare these two Models of prediction
#### How does it work?
- Change input value of carat and/or X, the two models will predict the price 

## Layout 

### Sidebar:  
- Slider 1: To select the value of carat
- Slider 2: To select the value of X 
- Show/hide prediction line of two model

### Main Panel:
- Plots of 2 models
- Value of prediction
- Which model is better in prediction of price

## Showtime  

```{r, echo = FALSE}

library(ggplot2)
library(shiny)

shinyApp(
  
  ui = fluidPage(
    titlePanel("Predict Diamond Price"),
  sidebarLayout(
    sidebarPanel(
      sliderInput("sliderCarat", "Carat", 0.2, 3.5, value = 0.7),
      checkboxInput("showModel1", "Show/Hide Carat Model", value = TRUE),
      sliderInput("sliderX", "X", 2.5, 10, value = 5),
      checkboxInput("showModel2", "Show/Hide X^4 Model", value = TRUE),
      tags$p("Click on Submit Button if you are ready"),
      submitButton("Submit")
    ),
    mainPanel(
      fluidRow(
        column(2, align="right",
               plotOutput(outputId = "plot1", width  = "500px",height = "400px"),  
               plotOutput(outputId = "plot2", width  = "500px",height = "400px")
        )),
      h4("Predicted Price from Carat Model:"),
      textOutput("pred1"),
      h5("R-quare of Carat Model:"),
      textOutput("R1"),
      h4("Predicted Price from X^4 Model:"),
      textOutput("pred2"),
      h5("R-quare of X^4 Model:"),
      textOutput("R2"),
      h4("Model that predicts better: "),
      textOutput("Better")
    )
  )
  ),
  
  server = function(input, output) {
  diamonds$x1 <- diamonds$x^4 #' create vector x1: x1=x^4
  model1 <- lm(price ~ carat, data = diamonds) #' Model to predict price on carat input
  model2 <- lm(price ~ x1, data = diamonds) #' Model to predict price on X input
  my_data <- data.frame(diamonds$carat,diamonds$x,diamonds$price, diamonds$x1)
   #' Reactive Input: sliderCarat
  model1pred <- reactive({
    caratInput <- input$sliderCarat
    predict(model1, newdata = data.frame(carat = caratInput))
  })
  #' Reactive Input: sliderX
  model2pred <- reactive({
    xInput <- input$sliderX
    predict(model2, newdata = data.frame(x = xInput, x1 = xInput^4))
  })
  
  #' Output Carat Model 
  output$plot1 <- renderPlot({
    caratInput <- input$sliderCarat
    
    plot(diamonds$carat, diamonds$price, xlab = "Carat", 
         ylab = "Price", 
         xlim = c(0.2, 3.5), ylim = c(300, 20000))
    if(input$showModel1){
      abline(model1, col = "red", lwd = 2)
    }
    points(caratInput, model1pred(), col = "blue", pch = 16, cex = 2)
  })
  
  #' Output X^4 Model
  output$plot2 <- renderPlot({
    xInput <- input$sliderX
    
    plot(diamonds$x1, diamonds$price, xlab = "X^4", 
         ylab = "Price", 
         xlim = c(40, 7000), ylim = c(300, 20000))
    if(input$showModel1){
      abline(model2, col = "red", lwd = 2)}
    points(xInput^4, model2pred(), col = "blue", pch = 16, cex = 2)
  })
  
  #' Out put predicted value of Carat model 
  output$pred1 <- renderText({
    model1pred()
  })
  # Output R-quare value of Carat Model
  output$R1 <- renderText({
    summary(model1)$r.squared
  })
  
  #' Out put predicted value of X^4 model 
  output$pred2 <- renderText({
    model2pred()
  })
  # Output R-quare value of Carat Model
  output$R2 <- renderText({
    summary(model2)$r.squared
  })
  
  #' Output Model that predict better based on R-Quare value
  
  output$Better <- renderText({ifelse(summary(model2)$r.squared > summary(model1)$r.squared,"X^4 Model","Carat Model")})
  
  },
  
  options = list(height = 500)
)
```
## Embedded Application

It's also possible to embed an entire Shiny application within an R Markdown document using the `shinyAppDir` function. This example embeds a Shiny application located in another directory:

```{r tabsets, echo=FALSE}
shinyAppDir(
  system.file("examples/06_tabsets", package = "shiny"),
  options = list(
    width = "100%", height = 550
  )
)
```

## Reference
### Code link: https://github.com/maiduong1012/Shiny-App
### App link: https://maiduong.shinyapps.io/multilinear/



